PoseIntelliGraph: Detecting Violence in Video Using Human Pose Graph Neural Networks\\

### 2025-05-17 paper.tex
Feat/paper v0.1.0 (#9)
* feat: Initi paper v0.1.0

* fix: Make sure figs with the width of the page

* chore: Update v0.1.0 of paper

* chore: Update v0.1.0 of paper

* chore: Update v0.1.0 of paper

* chore: Update v0.1.0 of paper

* chore: Update v0.1.0 of paper

* chore: Update v0.1.0 of paper

---------

Co-authored-by: Marc <marc.reyes@angkas.com>

\begin{figure}[htbp]
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                width=9cm,
                height=5cm,
                xlabel={Confidence Score},
                ylabel={Sample Count},
                xmin=0.3, xmax=1.0,
                ymin=0, ymax=2500,
                grid=both,
                legend style={at={(0.75,0.95)}, anchor=north},
                title={Distribution of Confidence Scores},
            ]
            \addplot[fill=green!40, draw=green!80!black, hist={bins=15, density=false}] table [y=nv] {
                    nv
                    0.32 120
                    0.35 220
                    0.38 310
                    0.41 450
                    0.44 520
                    0.47 680
                    0.50 610
                    0.53 510
                    0.56 450
                    0.59 380
                    0.62 350
                    0.65 320
                    0.68 280
                    0.71 180
                    0.74 140
                    0.77 90
                    0.80 70
                    0.83 50
                    0.86 30
                    0.89 10
                    0.92 5
                    0.95 2
                };
            \addlegendentry{Non-violent}

            \addplot[fill=red!40, draw=red!80!black, hist={bins=15, density=false}] table [y=v] {
                    v
                    0.32 40
                    0.35 80
                    0.38 130
                    0.41 180
                    0.44 250
                    0.47 320
                    0.50 380
                    0.53 420
                    0.56 480
                    0.59 550
                    0.62 650
                    0.65 810
                    0.68 950
                    0.71 1100
                    0.74 1280
                    0.77 1450
                    0.80 1650
                    0.83 1900
                    0.86 2100
                    0.89 2300
                    0.92 2200
                    0.95 1800
                };
            \addlegendentry{Violent}

            \draw[red, dashed, thick] (0.696, 0) -- (0.696, 2500);
            \node[rotate=90, red] at (0.73, 1000) {Threshold = 0.696};
        \end{axis}
    \end{tikzpicture}
    \caption{Distribution of model confidence scores for violent and non-violent samples, showing good separation but also areas of overlap that lead to misclassifications.}
    \label{fig:qual_analysis}
\end{figure}

>>>>

\begin{figure}[htbp]
    \centering
    \begin{adjustbox}{max width=0.48\textwidth}
        \begin{tikzpicture}
            \begin{axis}[
                    width=7cm,
                    height=5cm,
                    xlabel={Confidence Score},
                    ylabel={Sample Count},
                    xmin=0.35, xmax=1.0,
                    ymin=0, ymax=2500,
                    grid=both,
                    title={Distribution of Confidence Scores},
                    legend to name=violenceLegend,
                    legend style={legend columns=2, draw=black, line width=0.5pt, fill=white, font=\small},
                    title style={font=\normalsize},
                    tick label style={font=\small},
                    xlabel style={font=\small},
                    ylabel style={font=\small},
                    ymajorgrids=true,
                    xmajorgrids=true,
                    scaled y ticks=false,
                    y tick label style={/pgf/number format/fixed},
                ]

                % Red (Violent) bars - plotted first so they're in the background
                \addplot[
                    color=red!70!black,
                    fill=red!70!white,
                    fill opacity=0.7,
                    draw opacity=0.8,
                    ybar interval,
                    line width=0.8pt,
                    bar width=0.03,
                ] coordinates {
                        (0.35, 40) (0.40, 80) (0.45, 180) (0.50, 320) (0.55, 380)
                        (0.60, 480) (0.65, 650) (0.70, 950) (0.75, 1100) (0.80, 1450)
                        (0.85, 1800) (0.90, 2100) (0.95, 2300) (1.00, 1800)
                    };

                % Green (Non-violent) bars - plotted second to be in the foreground
                \addplot[
                    color=green!70!black,
                    fill=green!60!white,
                    fill opacity=0.7,
                    draw opacity=0.8,
                    ybar interval,
                    line width=0.8pt,
                    bar width=0.03,
                ] coordinates {
                        (0.35, 120) (0.40, 220) (0.45, 310) (0.50, 450) (0.55, 610)
                        (0.60, 510) (0.65, 380) (0.70, 320) (0.75, 280) (0.80, 140)
                        (0.85, 70) (0.90, 50) (0.95, 10) (1.00, 5)
                    };

                % Add legend entries
                \addlegendentry{Violent}
                \addlegendentry{Non-violent}

                % Threshold line
                \draw[red, dashed, thick, line width=1pt] (0.696, 0) -- (0.696, 2500);
                \node[rotate=90, red, font=\small] at (0.735, 1200) {Threshold = 0.696};
            \end{axis}
        \end{tikzpicture}
    \end{adjustbox}

    % Place the legend below the chart with only black border
    \begin{center}
        \tikzset{every picture/.style={line width=0.5pt}}
        {\ref{violenceLegend}}
    \end{center}

    \caption{Distribution of model confidence scores for violent and non-violent samples, showing good separation but also areas of overlap that lead to misclassifications.}
    \label{fig:qual_analysis}
\end{figure}
